---
title: "Highest-Scoring-Word"
author: "Humoon"
date: "`r Sys.Date()`"
output: html_document
---


```{r setup, include = FALSE}
source("../config/config.R")

## global options ===================================
knitr::opts_chunk$set(
  width = config$width,
  fig.width = config$fig.width,
  fig.asp = config$fig.asp,
  out.width = config$out.width,
  fig.align = config$fig.align,
  fig.path = config$fig.path,
  fig.show = config$fig.show,
  warn = config$warn,
  warning = config$warning,
  message = config$message,
  echo = config$echo,
  eval = config$eval,
  tidy = config$tidy,
  comment = config$comment,
  collapse = config$collapse,
  cache = config$cache,
  cache.comments = config$cache.comments,
  autodep = config$autodep
)
```

### Description

Given a string of words, you need to find the highest scoring word.

Each letter of a word scores points according to its position in the alphabet: `a = 1, b = 2, c = 3` etc.

You need to return the highest scoring word as a string.

If two words score the same, return the word that appears earliest in the original string.

All letters will be lowercase and all inputs will be valid.


### Solutions


#### Julia

```{julia}
# Highest-Scoring-Word.jl

using Test


"""
word 是字符串切割的产物，数据类型为 SubString{String}  
其父类为 AbstractString
"""
function get_score(word::AbstractString)::Int64
    # @show typeof(word)
    word |> collect .|> (char -> char - 'a' + 1) |> sum
end


function high(x::String)::String
    words = x |> split
    _, max_index = words .|> get_score |> findmax
    return words[max_index]
end


@test high("man i need a taxi up to ubud") == "taxi"
@test high("what time are we climbing up the volcano") == "volcano"
```

#### R

```{r}
# Highest-Scoring-Word.R

library(tidyverse)
library(testthat)


get_value <- function(word) {
  word %>%
    str_split("") %>%
    unlist() %>%
    map_int(~ match(.x, letters)) %>%
    sum()
}


high <- function(x) {
  words <- x %>%
    str_split(" ") %>%
    unlist()
  values <- words %>% map_int(get_value)
  words[which.max(values)]
}


# unit test
test_that("Sample Tests", {
  expect_equal(high("what time are we climbing up the volcano"), "volcano")
})

```

#### JavaScript

```{node}
/**
 * @module Highest-Scoring-Word
 */

const sum = require("../src/JavaScript/toolkit/Statistics").sum;

function get_score(word) {
  return sum(word.split('').map(c => c.charCodeAt() - 'a'.charCodeAt() + 1));
}

function high(x) {
  const words = x.split(' ');
  const values = words.map(get_score);
  return words[values.indexOf(Math.max(...values))];
}

console.log(high('what time are we climbing up the volcano'));
```

#### Python

```{python}
# Highest-Scoring-Word.py


#%%
def get_score(word):
    return sum([ord(c) - 96 for c in word])


#%%
def high(x):
    words = x.split()
    return max(words, key=get_score)


# %%
high("what time are we climbing up the volcano")

# %%

```
