---
title: "Your-order-please"
author: "Humoon"
date: "`r Sys.Date()`"
output: html_document
---


```{r setup, include = FALSE}
source("../config/config.R")

## global options ===================================
knitr::opts_chunk$set(
  width = config$width,
  fig.width = config$fig.width,
  fig.asp = config$fig.asp,
  out.width = config$out.width,
  fig.align = config$fig.align,
  fig.path = config$fig.path,
  fig.show = config$fig.show,
  warn = config$warn,
  warning = config$warning,
  message = config$message,
  echo = config$echo,
  eval = config$eval,
  tidy = config$tidy,
  comment = config$comment,
  collapse = config$collapse,
  cache = config$cache,
  cache.comments = config$cache.comments,
  autodep = config$autodep
)
```

### Description

Your task is to sort a given string. Each word in the string will contain a single number. This number is the position the word should have in the result.

Note: Numbers can be from 1 to 9. So 1 will be the first word (not 0).

If the input string is empty, return an empty string. The words in the input String will only contain valid consecutive numbers.

#### Examples

```
"is2 Thi1s T4est 3a"  -->  "Thi1s is2 3a T4est"
"4of Fo1r pe6ople g3ood th5e the2"  -->  "Fo1r the2 g3ood 4of th5e pe6ople"
""  -->  ""
```



### Solutions


#### Julia

```{julia}
using Pipe
using Test


function extract_number(s::AbstractString)::Int64
    @pipe match(r"\d", s).match |> parse(Int, _)
end

@assert extract_number("T4est") == 4 "Something wrong in extracting numbers."


function order(words::String)::String
    @pipe words |> split |> sort(_, by=extract_number) |> join(_, " ")
end

@test order("is2 Thi1s T4est 3a") == "Thi1s is2 3a T4est"
```

#### R

```{r}
## Your order, please

library(tidyverse)


#' 一个句子的各单词中含数字，按照数字的顺序对单词重排序
your_order <- function(sentence) {
  words <- sentence %>%
    str_split(" ") %>%
    unlist()

  numbers <- words %>%
    map_dbl(readr::parse_number) # 用parse_number()提取数字，不用正则

  words[order(numbers)] %>% str_c(collapse = " ")
}


library(testthat)
test_that("Example Test", {
  expect_equal(your_order("is2 Thi1s T4est 3a"), "Thi1s is2 3a T4est")
})

```

#### JavaScript

```{node}


function order(words) {
  parseNumber = s => parseInt(s.match(/\d/g));

  return words.split(" ")
    .sort((a, b) => parseNumber(a) - parseNumber(b))
    .join(" ");
}

console.log(order("is2 Thi1s T4est 3a"));

```
