---
title: "Decimal to Factorial and Back"
author: "Humoon"
date: "`r Sys.Date()`"
output: html_document
---


```{r setup, include = FALSE}
source("./config/config.R")

## global options ===================================
knitr::opts_chunk$set(
  width = config$width,
  fig.width = config$fig.width,
  fig.asp = config$fig.asp,
  out.width = config$out.width,
  fig.align = config$fig.align,
  fig.path = config$fig.path,
  fig.show = config$fig.show,
  warn = config$warn,
  warning = config$warning,
  message = config$message,
  echo = config$echo,
  eval = config$eval,
  tidy = config$tidy,
  comment = config$comment,
  collapse = config$collapse,
  cache = config$cache,
  cache.comments = config$cache.comments,
  autodep = config$autodep
)
```



### Description


Coding decimal numbers with factorials is a way of writing out numbers in a base system that depends on factorials, rather than powers of numbers.

In this system, the last digit is always `0` and is in base 0!. The digit before that is either `0 or 1` and is in base 1!. The digit before that is either `0, 1, or 2` and is in base 2!, etc. More generally, the nth-to-last digit is always `0, 1, 2, ..., n` and is in base n!.

Read more about it at: http://en.wikipedia.org/wiki/Factorial_number_system

#### Example
The decimal number `463` is encoded as `"341010"`, because:

463 = 3×5! + 4×4! + 1×3! + 0×2! + 1×1! + 0×0!

If we are limited to digits `0..9`, the biggest number we can encode is 10!-1 (= 3628799). So we extend `0..9` with letters `A..Z`. With these 36 digits we can now encode numbers up to 36!-1 (= 3.72 × 1041)

#### Task
We will need two functions. The first one will receive a decimal number and return a string with the factorial representation.

The second one will receive a string with a factorial representation and produce the decimal representation.

Given numbers will always be positive.


### Solution

#### R
```{r}
## Decimal-to-Factorial-and-Back.R

library(tidyverse)


codes <- "0123456789ABCDEFGHIJKLMNOPQRSTUVWXYZ" %>%
  str_split("") %>%
  unlist()


#' 将 0:35 的阶乘视为一组基，将参数向这组基分解出系数
#' @param nb 待分解的整数
#' @return 系数数组的字符串
dec2FactString <- function(nb) {
  # 先找最大的基
  max_base <- 1
  while (factorial(max_base + 1) <= nb) {
    max_base <- max_base + 1
  }

  # 从大到小，确定每个基对应的系数
  x <- character(0)
  for (i in max_base:0) {
    x[length(x) + 1] <- codes[nb %/% factorial(i) + 1]
    nb <- nb %% factorial(i)
  }

  x %>% str_c(collapse = "")
}

dec2FactString(463)



#' 已知系数和基，求和
#' @param str 系数数组的字符串
#' @return 加总后的整数
factString2Dec <- function(str) {
  # 逆序的系数向量
  factors <- str %>%
    str_split("") %>%
    unlist() %>%
    rev() %>%
    map_dbl(function(char) which(codes == char) - 1)

  # 基向量
  bases <- 0:(length(factors) - 1) %>% factorial()

  sum(factors * bases)
}

factString2Dec("341010")


library(testthat)
testing1 <- function(nb, expected) {
  actual <- dec2FactString(nb)
  expect_equal(actual, expected)
}
testing2 <- function(str, expected) {
  actual <- factString2Dec(str)
  expect_equal(actual, expected)
}

test_that("tests dec2FactString", {
  testing1(2982, "4041000")
  testing1(463, "341010")
  testing1(36288000, "A0000000000")
  testing1(3628800054, "76A0000021000")
  testing1(1273928000, "27A0533231100")
  testing1(220, "140200")
  testing1(1936295, "5301133210")
  testing1(81440635, "204365543010")
  testing1(14808485, "40721200210")
  testing1(3395, "4411210")
  testing1(92, "33100")
  testing1(4881, "6431110")
  testing1(174720, "424400000")
  testing1(5897, "11102210")
  testing1(1947, "2410110")
  testing1(1575088, "4303332200")
  testing1(49124, "115113100")
  testing1(9376317, "25742343110")
  testing1(449, "332210")
  testing1(112, "42200")
  testing1(64269, "145123110")
  testing1(6742089, "18515001110")
  testing1(86565208, "218474232200")
  testing1(1806792694, "3929024133200")
  testing1(12942219, "35576140110")
})

test_that("tests factString2Dec", {
  testing2("4041000", 2982)
  testing2("27A0533231100", 1273928000)
  testing2("341010", 463)
  testing2("65341010", 34303)
  testing2("1461330110", 555555)
  testing2("13573044440000", 7890123456)
  testing2("1630614043233100", 1849669781372)
  testing2("150636011110", 58322193)
  testing2("1662032340200", 741017980)
  testing2("194B99466413200", 145612691086)
  testing2("51465021000", 18702054)
  testing2("445212100", 185318)
  testing2("1000100", 722)
  testing2("522200", 664)
  testing2("2000", 12)
  testing2("64C0048313011110", 8269501168833)
  testing2("2455221000", 916134)
  testing2("10A739302433010", 92262000091)
  testing2("1A20254533200", 885536614)
  testing2("3855031110", 1440081)
  testing2("14D4831766411000", 1739585710590)
  testing2("331703501110", 131284689)
  testing2("86CB45050343200", 740991913678)
  testing2("112086032303100", 94394539820)
  testing2("30A3700211000", 1474663950)
  testing2("156B92750141010", 121660182223)
})

yTests <- function() {
  i <- 0
  while (i < 20) {
    n <- floor(runif(1, 1000000, 12166018222))
    act <- factString2Dec(dec2FactString(n))
    expect_equal(act, n)
    i <- i + 1
  }
}
test_that("Random tests", {
  yTests()
})
```


#### Julia
```{julia}
## Decimal-to-Factorial-and-Back.jl

using Pipe, Test


const code = ['0':'9'; 'A':'Z']
const encode = Dict(i - 1 => code[i] for i = 1:length(code))
const decode = Dict(code[i] => i - 1 for i = 1:length(code))


"""
将整数线性分解为一组基，返回系数连接成的字符串
"""
function dec2FactString(nb::Int)::String
    # 先找最大的基
    max_base = 1
    while factorial(max_base + 1) <= nb
        max_base += 1
    end

    # 从大到小，确定每个基对应的系数
    factors = ""
    for base ∈ max_base:-1:0
        factors *= encode[nb÷factorial(base)] # 这里的*表示字符串连接
        nb %= factorial(base)
    end

    factors
end

@test dec2FactString(463) == "341010"



"""
已知基（阶乘）和系数连接成的字符串，计算整数
"""
function factString2Dec(str::String)::Int
    # 逆序的系数向量
    factors = @pipe collect(str) .|> decode[_] |> reverse

    # 基向量，从 0! 到 max_base!
    bases = 0:(length(factors)-1) .|> factorial

    sum(factors .* bases)
end

@test factString2Dec("341010") == 463
```


#### JavaScript

```{node}

const naturalSequence = require("../../src/JavaScript/toolkit/Vector").naturalSequence;
const factorial = require("../../src/JavaScript/toolkit/Arithmetic").factorial;
const hadamardProduct = require("../../src/JavaScript/toolkit/Matrix").hadamardProduct;
const sum = require("../../src/JavaScript/toolkit/Statistics").sum;


// 字符串本身就是 iterator, 可以用索引 [] 访问
const code = "0123456789ABCDEFGHIJKLMNOPQRSTUVWXYZ";
const encode = new Map, decode = new Map;
for (let i = 0; i <= 35; i++) {
  encode.set(i, code[i]);
  decode.set(code[i], i);
}


function dec2FactString(nb) {
  // 寻找最大的基
  let maxBase = 1;
  while (factorial(maxBase + 1) <= nb) {
    maxBase++;
  }

  // 对应这组基的系数向量
  const factors = [];
  for (let i = maxBase; i >= 0; i--) {
    char = encode.get(Math.floor(nb / factorial(i)));
    factors.push(char);
    nb %= factorial(i);
  }

  return factors.join('');
}

console.log(dec2FactString(463));


function factString2Dec(string) {
  const factors = string.split('').reverse().map(char => decode.get(char));
  const bases = naturalSequence(string.length, start = 0).map(factorial);
  return sum(hadamardProduct(factors, bases));
}

console.log(factString2Dec("341010"));
```


