---
title: "Detect Pangram"
author: "Humoon"
date: "`r Sys.Date()`"
output: html_document
---


```{r setup, include = FALSE}
source("./config/config.R")

## global options ===================================
knitr::opts_chunk$set(
  width = config$width,
  fig.width = config$fig.width,
  fig.asp = config$fig.asp,
  out.width = config$out.width,
  fig.align = config$fig.align,
  fig.path = config$fig.path,
  fig.show = config$fig.show,
  warn = config$warn,
  warning = config$warning,
  message = config$message,
  echo = config$echo,
  eval = config$eval,
  tidy = config$tidy,
  comment = config$comment,
  collapse = config$collapse,
  cache = config$cache,
  cache.comments = config$cache.comments,
  autodep = config$autodep
)
```



### Description

A pangram is a sentence that contains every single letter of the alphabet at least once. For example, the sentence "The quick brown fox jumps over the lazy dog" is a pangram, because it uses the letters A-Z at least once (case is irrelevant).

Given a string, detect whether or not it is a pangram. Return True if it is, False if not. Ignore numbers and punctuation.


### Solution

#### R
```{r}
## Detect Pangram (全字母短句)

library(tidyverse)
library(magrittr)


#' 检查字符串中是否包含全部的英文字母（忽略大小写）
is_pangram <- function(string) {
  # string 中包含的所有字母（小写）
  chars <- string %>%
    tolower() %>%
    str_split("") %>%
    unlist() %>%
    unique()

  # 向量化检查
  letters %in% chars %>% all()
}


library(testthat)
test_that("Example Test Cases", {
  pangram <- "The quick, brown fox jumps over the lazy dog!"
  expect_equal(is_pangram(pangram), TRUE)
})
```


#### Julia
```{julia}


"""
检测字符串是否包含所有26个字母
"""
function is_pangram(string)
  # all() 接收 iterator，里面是一个 BitVector
  all('a':'z' .∈ lowercase(string))
end


using Test
@test is_pangram("The quick, brown fox jumps over the lazy dog!") == true
```


#### JavaScript

```{node}

const letters = require("../../src/JavaScript/toolkit/CharacterObject").letters;

function isPangram(string) {
  // const letters = [...Array(26)].map((_, i) => String.fromCharCode(i + 97));
  return letters.every(c => string.toLowerCase().includes(c));
}


console.log(isPangram("The quick, brown fox jumps over the lazy dog!"));
```


