---
title: "Directions Reduction"
author: "Humoon"
date: "`r Sys.Date()`"
output: html_document
---


```{r setup, include = FALSE}
source("./config/config.R")

## global options ===================================
knitr::opts_chunk$set(
  width = config$width,
  fig.width = config$fig.width,
  fig.asp = config$fig.asp,
  out.width = config$out.width,
  fig.align = config$fig.align,
  fig.path = config$fig.path,
  fig.show = config$fig.show,
  warn = config$warn,
  warning = config$warning,
  message = config$message,
  echo = config$echo,
  eval = config$eval,
  tidy = config$tidy,
  comment = config$comment,
  collapse = config$collapse,
  cache = config$cache,
  cache.comments = config$cache.comments,
  autodep = config$autodep
)
```



### Description

#### Once upon a time, on a way through the old wild mountainous west,…
… a man was given directions to go from one point to another. The directions were "NORTH", "SOUTH", "WEST", "EAST". Clearly "NORTH" and "SOUTH" are opposite, "WEST" and "EAST" too.

Going to one direction and coming back the opposite direction right away is a needless effort. Since this is the wild west, with dreadful weather and not much water, it's important to save yourself some energy, otherwise you might die of thirst!

#### How I crossed a mountainous desert the smart way.
The directions given to the man are, for example, the following (depending on the language):

```
["NORTH", "SOUTH", "SOUTH", "EAST", "WEST", "NORTH", "WEST"].
or
{ "NORTH", "SOUTH", "SOUTH", "EAST", "WEST", "NORTH", "WEST" };
or
[North, South, South, East, West, North, West]
```

You can immediately see that going "NORTH" and immediately "SOUTH" is not reasonable, better stay to the same place! So the task is to give to the man a simplified version of the plan. A better plan in this case is simply:

```
["WEST"]
or
{ "WEST" }
or
[West]
```


#### Other examples:

In ["NORTH", "SOUTH", "EAST", "WEST"], the direction "NORTH" + "SOUTH" is going north and coming back right away.

The path becomes ["EAST", "WEST"], now "EAST" and "WEST" annihilate each other, therefore, the final result is [] (nil in Clojure).

In ["NORTH", "EAST", "WEST", "SOUTH", "WEST", "WEST"], "NORTH" and "SOUTH" are not directly opposite but they become directly opposite after the reduction of "EAST" and "WEST" so the whole path is reducible to ["WEST", "WEST"].

#### Task

Write a function dirReduc which will take an array of strings and returns an array of strings with the needless directions removed (W<->E or S<->N side by side).

#### See more examples in "Sample Tests:"

#### Notes

Not all paths can be made simpler. The path ["NORTH", "WEST", "SOUTH", "EAST"] is not reducible. "NORTH" and "WEST", "WEST" and "SOUTH", "SOUTH" and "EAST" are not directly opposite of each other and can't become such. Hence the result path is itself : ["NORTH", "WEST", "SOUTH", "EAST"].
if you want to translate, please ask before translating.


### Solution

#### R
```{r}
library(tidyverse)
library(magrittr)


dirReduc <- function(arr) {
  # 用 named vector 起到其他语言中 Dict/Map 的作用
  opposite_dir <- c("NORTH", "SOUTH", "EAST", "WEST") %>%
    set_names(c("SOUTH", "NORTH", "WEST", "EAST"))

  stack <- character(0)

  for (step in arr) {
    n <- length(stack)
    if (n > 0 && opposite_dir[step] == stack[n]) {
      stack <- stack[-n]
    } else {
      stack[n + 1] <- step
    }
  }

  stack
}



library(testthat)
testing <- function(ls, expected) {
  actual <- dirReduc(ls)
  expect_equal(actual, expected)
}
test_that("tests", {
  a <- c("NORTH", "SOUTH", "SOUTH", "EAST", "WEST", "NORTH", "WEST")
  testing(a, c("WEST"))
  a <- c("NORTH", "WEST", "SOUTH", "EAST")
  testing(a, c("NORTH", "WEST", "SOUTH", "EAST"))
  a <- c("NORTH", "SOUTH", "SOUTH", "EAST", "WEST", "NORTH", "NORTH")
  testing(a, c("NORTH"))
})
```


#### Julia
```{julia}


# 有对应关系时，经常可以用 Dict 化简代码
const OppositeDir = Dict(
  "NORTH" => "SOUTH",
  "EAST" => "WEST",
  "SOUTH" => "NORTH",
  "WEST" => "EAST"
)


"""
简化无效路径
"""
function dir_reduc(arr)
  stack = []

  for step ∈ arr
    # short-circuit logic：当stack为空时，stack[end]根本不会运行
    if !isempty(stack) && (stack[end] => step) ∈ OppositeDir
      pop!(stack)
    else
      push!(stack, step)
    end
  end

  stack
end


using Test
@test dir_reduc(["NORTH", "SOUTH", "SOUTH", "EAST", "WEST", "NORTH", "WEST"]) == ["WEST"]


```


#### JavaScript

```{node}
function dirReduc(arr) {

  const opposite_dir = new Map([
    ["NORTH", "SOUTH"], ["SOUTH", "NORTH"],
    ["EAST", "WEST"], ["WEST", "EAST"]]);

  const stack = [];

  for (step of arr) {
    let n = stack.length;
    if (n !== 0 && opposite_dir.get(step) === stack[n - 1]) {
      stack.pop();
    } else {
      stack.push(step);
    }
  }

  return stack;
}



console.log(dirReduc(["NORTH", "SOUTH", "SOUTH", "EAST", "WEST", "NORTH", "WEST"]));



```


