---
title: "Game Hit the target"
author: "Humoon"
date: "`r Sys.Date()`"
output: html_document
---


```{r setup, include = FALSE}
source("./config/config.R")

## global options ===================================
knitr::opts_chunk$set(
  width = config$width,
  fig.width = config$fig.width,
  fig.asp = config$fig.asp,
  out.width = config$out.width,
  fig.align = config$fig.align,
  fig.path = config$fig.path,
  fig.show = config$fig.show,
  warn = config$warn,
  warning = config$warning,
  message = config$message,
  echo = config$echo,
  eval = config$eval,
  tidy = config$tidy,
  comment = config$comment,
  collapse = config$collapse,
  cache = config$cache,
  cache.comments = config$cache.comments,
  autodep = config$autodep
)
```



### Description


given a matrix `n x n` , determine if the arrow is directed to the target (x).
There will be only 1 arrow '>' and 1 target 'x'
An empty spot will be denoted by a space " ", the target with a cross "x", and the scope ">"

#### Examples:

given matrix 4x4:

```
[

  [' ', ' ', ' ', ' '],

  [' ', ' ', ' ', ' '], --> return true

  [' ', '>', ' ', 'x'],

  [' ', ' ', ' ', ' ']

] 
```

given matrix 4x4:

```
[

  [' ', ' ', ' ', ' '],

  [' ', '>', ' ', ' '], --> return false

  [' ', ' ', ' ', 'x'],

  [' ', ' ', ' ', ' ']

] 
```

given matrix 4x4:

```
[

  [' ', ' ', ' ', ' '],

  [' ', 'x', '>', ' '], --> return false

  [' ', '', ' ', ' '],

  [' ', ' ', ' ', ' ']

] 
```

In this example, only a 4x4 matrix was used, the problem will have matrices of dimensions from 2 to 7
Happy hacking as they say!


### Solution

#### R
```{r}
library(tidyverse)


solution <- function(M) {
  # 将M沿列展开为向量的一维坐标
  arrow_index <- match(">", M)
  target_index <- match("x", M)

  # 二维坐标中的行
  arrow_i <- arrow_index %% nrow(M)
  target_i <- target_index %% nrow(M)

  arrow_i == target_i && arrow_index < target_index
}


M <- c(rep(" ", 17), ">", " ", "x", rep(" ", 5)) %>%
  matrix(nrow = 5, ncol = 5, byrow = TRUE)

solution(M)
```


#### Julia
```{julia}
function solution(A::Matrix{Char})::Bool
  arrow_indice = findfirst(c -> c == '>', A)
  target_indice = findfirst(c -> c == 'x', A)

  in_same_line = arrow_indice[1] == target_indice[1]
  order_is_right = arrow_indice[2] < target_indice[2]
  in_same_line && order_is_right
end


A = [
  ' ' ' ' ' ' ' ' ' '
  ' ' ' ' ' ' ' ' ' '
  ' ' ' ' ' ' ' ' ' '
  ' ' ' ' '>' ' ' 'x'
  ' ' ' ' ' ' ' ' ' '
]

solution(A)
```


#### JavaScript

```{node}
const solution = function (mtrx) {
  for (let row of mtrx) {
    let scope = row.indexOf('>');
    let target = row.indexOf('x');
    if (target > -1 && scope > -1 && scope < target) return true;
  }
  return false;
};


console.log(solution([
  [' ', ' ', ' ', ' ', ' '],
  [' ', ' ', ' ', ' ', ' '],
  [' ', ' ', ' ', ' ', ' '],
  [' ', ' ', '>', ' ', 'x'],
  [' ', ' ', '', ' ', ' ']
]));
```


