---
title: "N-th Fibonacci"
author: "Humoon"
date: "`r Sys.Date()`"
output: html_document
---


```{r setup, include = FALSE}
source("./config/config.R")

## global options ===================================
knitr::opts_chunk$set(
  width = config$width,
  fig.width = config$fig.width,
  fig.asp = config$fig.asp,
  out.width = config$out.width,
  fig.align = config$fig.align,
  fig.path = config$fig.path,
  fig.show = config$fig.show,
  warn = config$warn,
  warning = config$warning,
  message = config$message,
  echo = config$echo,
  eval = config$eval,
  tidy = config$tidy,
  comment = config$comment,
  collapse = config$collapse,
  cache = config$cache,
  cache.comments = config$cache.comments,
  autodep = config$autodep
)
```



### Description

I love Fibonacci numbers in general, but I must admit I love some more than others.

I would like for you to write me a function that when given a number (n) returns the n-th number in the Fibonacci Sequence.

For example:

```
nthfibo(4) == 2
```

Because 2 is the 4th number in the Fibonacci Sequence.

For reference, the first two numbers in the Fibonacci sequence are 0 and 1, and each subsequent number is the sum of the previous two.


#### 要点

斐波那契数列相邻两项的变化，可以通过一个线性变换得到，即

$$
\begin{bmatrix}
 a_n\\
a_{n+1}
\end{bmatrix} = \begin{bmatrix}
 0 & 1\\
1 & 1
\end{bmatrix} \begin{bmatrix}
 a_{n-1}\\
a_{n}
\end{bmatrix}
$$


### Solution

#### R
```{r}
library(tidyverse)
Matrix <- modules::use("../../src/R/toolkit/Matrix.R")


nthfibo <- function(n) {
  matrix_pow <- Matrix$`%^%`
  F <- c(0, 1, 1, 1) %>% matrix(2)

  (matrix_pow(F, n - 1) %*% c(0, 1))[1, 1]
}

nthfibo(4) == 2
```


#### Julia
```{julia}

# 斐波那契数列对应的线性变换
F = [0 1; 1 1]

nthfibo(n::Integer) = (F^(n-1)*[0, 1])[1]

using Test
@test nthfibo(4) == 2
```


