---
title: "Twice linear"
author: "Humoon"
date: "`r Sys.Date()`"
output: html_document
---


```{r setup, include = FALSE}
source("./config/config.R")

## global options ===================================
knitr::opts_chunk$set(
  width = config$width,
  fig.width = config$fig.width,
  fig.asp = config$fig.asp,
  out.width = config$out.width,
  fig.align = config$fig.align,
  fig.path = config$fig.path,
  fig.show = config$fig.show,
  warn = config$warn,
  warning = config$warning,
  message = config$message,
  echo = config$echo,
  eval = config$eval,
  tidy = config$tidy,
  comment = config$comment,
  collapse = config$collapse,
  cache = config$cache,
  cache.comments = config$cache.comments,
  autodep = config$autodep
)
```



### Description


Consider a sequence u where u is defined as follows:

1. The number `u(0) = 1` is the first one in u.
2. For each `x` in `u`, then `y = 2 * x + 1` and `z = 3 * x + 1` must be in `u` too.
3. There are no other numbers in u.

Ex: `u = [1, 3, 4, 7, 9, 10, 13, 15, 19, 21, 22, 27, ...]`

1 gives 3 and 4, then 3 gives 7 and 10, 4 gives 9 and 13, then 7 gives 15 and 22 and so on...

#### Task

Given parameter `n` the function `dbl_linear` (or `dblLinear`...) returns the element `u(n)` of the ordered (with <) sequence `u` (so, there are no duplicates).

#### Example

`dbl_linear(10) should return 22`

#### Note
Focus attention on efficiency


### Solution

#### R
```{r}
library(tidyverse)

dblLinear <- function(n) {
  u <- 1
  i <- 1
  j <- 1
  while (length(u) < n + 1) {
    y <- 2 * u[i] + 1
    z <- 3 * u[j] + 1
    if (y < z) {
      u[length(u) + 1] <- y
      i <- i + 1
    } else if (y > z) {
      u[length(u) + 1] <- z
      j <- j + 1
    } else {
      u[length(u) + 1] <- y
      i <- i + 1
      j <- j + 1
    }
  }
  u[n + 1]
}


library(testthat)
testing <- function(n, expected) {
  actual <- dblLinear(n)
  expect_equal(actual, expected)
}
test_that("tests", {
  testing(10, 22)
  testing(20, 57)
  testing(50, 175)
})
```


#### JavaScript

```{node}
function dblLinear(n) {
    let u = [1], i = 0, j = 0; //two pointer
    while (u.length < n + 1) {
        let newTerm = Math.min(2 * u[i] + 1, 3 * u[j] + 1);
        u.push(newTerm)
        if (newTerm === 2 * u[i] + 1) i++;
        if (newTerm === 3 * u[j] + 1) j++;
    }
    return u[n];
}

console.log(dblLinear(10));

module.exports = dblLinear;
```


