---
title: "Where my anagrams at"
author: "Humoon"
date: "`r Sys.Date()`"
output: html_document
---


```{r setup, include = FALSE}
source("./config/config.R")

## global options ===================================
knitr::opts_chunk$set(
  width = config$width,
  fig.width = config$fig.width,
  fig.asp = config$fig.asp,
  out.width = config$out.width,
  fig.align = config$fig.align,
  fig.path = config$fig.path,
  fig.show = config$fig.show,
  warn = config$warn,
  warning = config$warning,
  message = config$message,
  echo = config$echo,
  eval = config$eval,
  tidy = config$tidy,
  comment = config$comment,
  collapse = config$collapse,
  cache = config$cache,
  cache.comments = config$cache.comments,
  autodep = config$autodep
)
```



### Description


What is an anagram? Well, two words are anagrams of each other if they both contain the same letters. For example:

```
'abba' & 'baab' == true

'abba' & 'bbaa' == true

'abba' & 'abbba' == false

'abba' & 'abca' == false
```

Write a function that will find all the anagrams of a word from a list. You will be given two inputs a word and an array with words. You should return an array of all the anagrams or an empty array if there are none. For example:

```
anagrams('abba', ['aabb', 'abcd', 'bbaa', 'dada']) => ['aabb', 'bbaa']

anagrams('racer', ['crazer', 'carer', 'racar', 'caers', 'racer']) => ['carer', 'racer']

anagrams('laser', ['lazing', 'lazy',  'lacer']) => []
```

#### Note for Go
For Go: Empty string slice is expected when there are no anagrams found.


### Solution

#### R
```{r}
library(tidyverse)

#' 挑选出 words 中所含字母与 word 相同的元素
anagrams <- function(word, words) {
  rearrange <- function(w) {
    w %>%
      str_split("") %>%
      unlist() %>%
      sort() %>%
      str_c(collapse = "")
  }

  # 该问题的核心就是一步 filter
  words %>%
    keep(function(element) rearrange(element) == rearrange(word))
}

anagrams("abba", c("aabb", "abcd", "bbaa", "dada"))
```


#### Julia
```{julia}
function anagrams(word, words)
  rearrange(string) = collect(string) |> sort |> join
  filter(w -> rearrange(w) == rearrange(word), words)
end

anagrams("abba", ["aabb", "abcd", "bbaa", "dada"])

```


#### JavaScript

```{node}
function anagrams(word, words) {
  rearrange = string => string.split('').sort().join('');
  return words.filter(w => rearrange(w) === rearrange(word));
}

console.log(anagrams("abba", ["aabb", "abcd", "bbaa", "dada"]));
```


